\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}

% Remove page number
\pagestyle{empty}

\begin{document}

\noindent
\today

\vspace{0.5cm}

\noindent
\textbf{To:} The Editor-in-Chief\\
\textbf{Journal:} Entertainment Computing\\
\textbf{Publisher:} Elsevier

\vspace{0.5cm}

\noindent
Dear Editor,

\vspace{0.3cm}

We are pleased to submit our manuscript entitled \textbf{``DreamWeaver: A Gamified Dream Journaling and Analysis Platform for Mental Wellness Through Interactive AI-Powered Features''} for consideration as a full research article in \textit{Entertainment Computing}.

\vspace{0.3cm}

\textbf{Problem Statement.}
Dream journaling offers significant therapeutic benefits for mental wellness, yet traditional applications suffer from critically poor user adherence---only 31\% of users remain active after seven days. The core challenge is the lack of immediate feedback and sustained motivation mechanisms. No prior work has systematically integrated AI-powered dream interpretation with entertainment computing principles to address this adherence problem, representing both a research gap and a barrier to realizing therapeutic potential at scale.

\vspace{0.3cm}

\textbf{Novel Contributions.}
This paper presents DreamWeaver, a gamified dream journaling platform that integrates AI-powered interpretation with entertainment computing mechanisms. Key innovations include:

\begin{itemize}
    \item \textbf{Integrated Ecosystem:} Unified platform combining AI interpretation (Gemini, DALL-E 2) with 16 interactive features across five design pillars for content-focused engagement.
    \item \textbf{Empirical Validation:} 14-day study (N=147) achieving 69.4\% retention (double typical rates) with 49-point wellness improvements for high-engagement users (p<.001, $\eta^2$=.85).
    \item \textbf{Design Insights:} ``Hard Fun'' phenomenon and ecosystem effects (Features Used r=.932) provide actionable principles for entertainment-health integration.
\end{itemize}

\vspace{0.3cm}

\textbf{Fit to Entertainment Computing.}
This work directly addresses \textit{Entertainment Computing}'s focus on interactive entertainment systems applied beyond leisure. We demonstrate how entertainment computing principles---immediate feedback loops, adaptive challenges, creative expression, and achievement progression---transform low-adherence therapeutic practice into sustained engagement with measurable wellness outcomes. This contributes to advancing entertainment computing as a serious research domain with real-world impact.

\vspace{0.3cm}

\textbf{Ethics, Originality, and Compliance.}
We confirm that this work is original, not under review elsewhere, approved by all authors and KUET's IRB with informed consent from all participants, GDPR-compliant with AES-256-CBC encryption, and presents no conflicts of interest.

\vspace{0.3cm}

We believe this work will be of strong interest to \textit{Entertainment Computing} readers working at the intersection of interactive systems, AI-driven experiences, user engagement, and applied computing for human wellbeing. We look forward to your consideration and welcome any feedback during the review process.

\vspace{0.5cm}

\noindent
Sincerely,

\vspace{0.3cm}

\noindent
\textbf{Adit Mugdha Das} (Corresponding Author)\\
Department of Computer Science and Engineering\\
Khulna University of Engineering and Technology\\
Khulna, Bangladesh\\
Email: \href{mailto:aditmugdhadas@gmail.com}{aditmugdhadas@gmail.com}

\vspace{0.2cm}

\noindent
On behalf of all authors:\\
Adit Mugdha Das and Kazi Saeed Alam

\end{document}
