\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{url}
\usepackage{titlesec}
\usepackage{enumitem}

% Remove page number
\pagestyle{empty}

% Adjust spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}

\begin{document}

% Journal info
\textbf{Submitted to:} Entertainment Computing

\vspace{0.5cm}

% Title
\begin{center}
{\LARGE \textbf{DreamWeaver: A Gamified Dream Journaling and Analysis Platform for Mental Wellness Through Interactive AI-Powered Features}}
\end{center}

\vspace{1cm}

% Authors
\section*{Authors}

\textbf{Adit Mugdha Das} (Corresponding Author)\\
Department of Computer Science and Engineering\\
Khulna University of Engineering and Technology\\
Khulna, Bangladesh\\
Email: \href{mailto:aditmugdhadas@gmail.com}{aditmugdhadas@gmail.com}

\vspace{0.5cm}

\textbf{Kazi Saeed Alam}\\
Assistant Professor\\
Department of Computer Science and Engineering\\
Khulna University of Engineering and Technology\\
Khulna, Bangladesh\\
Email: \href{mailto:saeed.utsha@gmail.com}{saeed.utsha@gmail.com}

\vspace{1cm}

% Contact Information
\section*{Corresponding Author}

\textbf{Name:} Adit Mugdha Das\\
\textbf{Email:} \href{mailto:aditmugdhadas@gmail.com}{aditmugdhadas@gmail.com}\\
\textbf{Institution:} Department of Computer Science and Engineering, Khulna University of Engineering and Technology, Khulna, Bangladesh

\vspace{1cm}

% Funding
\section*{Funding}

This research received no external funding.

\vspace{1cm}

% Conflict of Interest
\section*{Conflict of Interest}

The authors declare no conflict of interest.

\vspace{1cm}

% Acknowledgements
\section*{Acknowledgements}

We thank all study participants for their engagement and feedback during the 14-day field study. This research was conducted at the Department of Computer Science and Engineering, Khulna University of Engineering and Technology, Bangladesh.

\vspace{1cm}

% Data and Code Availability
\section*{Data and Code Availability}

Due to the sensitive and personal nature of dream content and mental wellness data, raw participant-level data cannot be publicly shared. Aggregated statistics, anonymized summaries, and analysis scripts are available from the corresponding author upon reasonable request.

The source code and system implementation for DreamWeaver are publicly available at:\\
\url{https://github.com/Adit-Mugdha-das/DreamWeaver}

\vspace{1cm}

% Ethics Statement
\section*{Ethics Statement}

This study received ethical approval from the Institutional Review Board of Khulna University of Engineering and Technology (KUET). All participants provided informed consent before enrollment. Data were encrypted (AES-256-CBC), stored with anonymous IDs, and handled in compliance with GDPR privacy standards.

\end{document}
